Automatic Generation of Knowledge Representation

### 2012-12-27 ontologies/paper.tex
Added pictures

@@

\subsection{Feature Engenieering component}
This corresponds to the second step of the preprocessing. In this step the texts are pruned and transformed into feature vectors.\\
Each document pass through the following filters:

>>>>

\begin{figure*}[]
  \centering
    \includegraphics[scale=0.2]{pics/problem.jpg}
    \caption{Problem Diagram}
   \label{fig:problem}  
\end{figure*}

@@

\subsection{Feature Engenieering component}

This corresponds to the second step of the preprocessing. In this step the texts are pruned and transformed into feature vectors (Figure ~\ref{fig:eng_component} ).\\
Each document pass through the following filters:

\begin{figure*}[]
  \centering
    \includegraphics[scale=0.2]{pics/eng_component.jpg}
    \caption{Feature Engenieering component}
   \label{fig:eng_component}  
\end{figure*}
